### 2020-01-10 README.Rmd
Add Travis CI?

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh///master?urlpath=rstudio)

@@

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
remotes::install_github("/")
```

@@

**Data :** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse

>>>>

[![Travis build status](https://travis-ci.org/mbjoseph/secmr.svg?branch=master)](https://travis-ci.org/mbjoseph/secmr)

@@

```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("mbjoseph/secmr")
```

@@
